---
title: "Study 2"
format:
    html:
        author:
            - name: "Filipa de Almeida"
              affiliation: UCP
            - name: "Cristina Mendonça"
              affiliation: LIP
            - name: "Vitória Melita"
              affiliation: FP-UL
            - name: "João O. Santos"
              affiliation: ISPA
---

``` {r, setup}
library(ggplot2)
library(parameters)
# knitr loaded by pretty_tables.R

# General options
options(digits = 3, emmeans = list(summary = list(digits = 3)))

# Run scripts
source("run_all.R")
# Source utility function
source("../../utils/pretty_tables.R")
```



# Descriptives



## Initial Rating

``` {r}
ggplot(ds, aes(x = initial_rating, fill = ethnicity)) +
geom_density(alpha = 0.5) +
theme_classic()
```



## WOA + Trust + Advisor


::: {.panel-tabset group="Graph"}

### WOA ~ Advisor

``` {r}
ggplot(ds, aes(x = WOA, fill = advisor)) +
geom_density(alpha = 0.5) +
xlim(-1.5, 1.5) +
theme_classic()
```


### Updated ~ Trust + Advisor (Step #1)

``` {r}
ggplot(voi, aes(x = Trust, fill = updated)) +
geom_density(alpha = 0.50) +
facet_wrap(~ advisor, nrow = 3) +
theme_classic()
```

``` {r}
ggplot(voi, aes(x = Trust, y = as.numeric(updated), color = advisor)) +
geom_jitter(height = 0.05, width = 0, alpha = 0.3) +
geom_smooth(method = "glm", method.args = list(family = "binomial"),
            se = FALSE, fullrange = TRUE, show.legend = FALSE) +
theme_classic()
```


### WOA ~ Trust + Advisor (Step #2)


``` {r}
g_ds <- subset(voi, updated)
ggplot(g_ds, aes(x = Trust, y = WOA, color = advisor)) +
geom_point(alpha = 0.50) +
geom_smooth(method = "lm", se = FALSE, show.legend = FALSE) +
ylim(-1.5, 1.5) +
theme_classic()
```

:::




# Racial Bias

> 1) The probability of being invited for an interview will be higher for
> British candidates than for Roma candidates, indicating a main effect of
> ethnicity (replicating study 1).

H1 is not supported, as there is no significant main effect of ethnicity
on initial ratings.



## ANOVA

``` {r}
pretty_table(nice(m_h1))
```



## Estimated Marginal Means


::: {.panel-tabset group="Group"}

### Overall

``` {r}
pretty_table(emm_h1[[1]])
```


### Ethnicity

``` {r}
pretty_table(emm_h1[[2]])
```

:::




# Egocentric Discounting

> 2) Participants’ final judgments will align more closely with their own
> initial probabilities than with the advice received, demonstrating
> egocentric discounting (Yaniv & Kleinberger, 2000) (replicating study 1).

H2 is supported, as participants' final judgments remained closer to
their initial ratings than to the advice received, indicated by a
significant intercept. There is also marginal evidence that egocentric
discounting is greater when the advisor is an uncertified AI system than
when it is a human. Despite there being no significant differences, in
our sample, the estimated marginal means follow the expected pattern:
uncertified AI > certified AI > human. Still, there is no evidence that
this trend is present in the population, just marginal evidence that
there is more egocentric discounting with the uncertified AI than with a
human advisor.



## ANOVA

``` {r}
pretty_table(nice(m_h2, intercept = TRUE))
```



## Estimated Marginal Means


::: {.panel-tabset group="Group"}

### Overall

``` {r}
pretty_table(emm_h2[[1]])
```


### Advisor

``` {r}
pretty_table(emm_h2[[2]])
```

:::



## Multiple Comparisons

``` {r}
pretty_table(emm_h2[[3]])
```




# WOA: Two-Step Hurdle Model

> 3) The weight of advice (WOA) will be higher for a human advisor than an AI
> advisor with no CE certification (replicating Study 1).
> 4) The WOA will be higher for an AI with a certification label than an AI
> with no certification label.

Regarding Step 1, there is no significant evidence that the probability
of updating varies between advisors. For Step 2, there is a marginal
main effect of advisor on the magnitude of the update; specifically, the
update is marginally greater for human advisors than for AI systems. H4
is not supported as there is no significant difference between the
certified and non-certified AI systems.



## Step #1: Probability of Updating


### ANOVA

``` {r}
pretty_table(nice(m_h3h4_1))
```


### Estimated Marginal Means

::: {.panel-tabset group="Group"}

#### Overall

``` {r}
pretty_table(emm_h3h4_1[[1]])
```

#### Advisor

``` {r}
pretty_table(emm_h3h4_1[[2]])
```

:::



## Step #2: Magnitude of the Update


### ANOVA

``` {r}
pretty_table(nice(m_h3h4_2))
```

### Estimated Marginal Means

::: {.panel-tabset group="Group"}

#### Overall

``` {r}
pretty_table(emm_h3h4_2[[1]])
```

#### Advisor

``` {r}
pretty_table(emm_h3h4_2[[2]])
```

:::


### Multiple Comparisons

``` {r}
pretty_table(emm_h3h4_2[[3]])
```




# Perceived Trust

> 5) Trust in the advisor will be higher for an AI with a certification
> label than an AI with no certification label.

H5 is not supported. While there is a strong main effect of advisor type
on trust, this is driven by higher trust in human employees compared to
both AI systems. There is no significant difference in trust between
certified and non-certified AI systems.



## ANOVA

``` {r}
pretty_table(nice(m_h5))
```



## Estimated Marginal Means

::: {.panel-tabset group="Group"}


### Overall

``` {r}
pretty_table(emm_h5[[1]])
```


### Advisor

``` {r}
pretty_table(emm_h5[[2]])
```

:::



## Multiple Comparisons
``` {r}
pretty_table(emm_h5[[3]])
```


# Mediation Analysis

> 6) Higher trust in the advisor will be associated with a higher WOA.
> 7) Trust in the advisor will mediate the relationship between the type of
> advisor and WOA.

For the probability of updating, there is a significant indirect effect
through trust despite the absence of a significant total effect. For the
magnitude of the update, trust significantly mediates the relationship
between advisor type and WOA, and the total effect is also significant.



## Step #1: Hurdle Mediation

``` {r}
pretty_table(parameters(m_b_1, effects = "fixed", exponentiate = TRUE))
```

``` {r}
#| code-fold: false
summary(h7_1)
```



## Step #2: Magnitude Mediation

``` {r}
pretty_table(parameters(m_b_2, effects = "fixed"))
```

``` {r}
#| code-fold: false
summary(h7_2)
```
